2.4 PRNT50

### 2024-05-17 2_scripts/2.4 PRNT50.qmd
Update PRNT50 analysis (unfinished)

table(APLs$pos_abbott_s, APLs$pos_abbott_s2, useNA = 'ifany')
```
## 3. Making the Plot

@@

tb_abbs_melt<-reshape2::melt(select(tb_abbs, -c(2:4)), 
                        id.vars = c("samplemonth"),
                        variable.name = "COI",
                        value.name = "prop")

p09<-tb_abbs_melt %>%
  ggplot(aes(x=samplemonth, y=prop, group=COI, colour=COI)) +
  geom_point(aes(colour=COI)) +
  geom_line(aes(colour=COI))  +
  theme_bw() 
p09
```

>>>>

table(APLs$pos_abbott_s, APLs$pos_abbott_s2, useNA = 'ifany')
```
### Apply COI to CBS (Roche-S) data
```{r}

```

## 3. Making the Plot

@@

tb_abbs_melt<-reshape2::melt(select(tb_abbs, -c(2:4)), 
                        id.vars = c("samplemonth"),
                        variable.name = "COI",
                        value.name = "prop")
```

## 3.2 Making the Plot
```{r}
# APL
p09<-tb_abbs_melt %>%
  ggplot(aes(x=samplemonth, y=prop, group=COI, colour=COI)) +
  geom_point(aes(colour=COI)) +
  geom_line(aes(colour=COI))  +
  theme_bw() 
p09
```
